Multi-Index and Multi-Level Monte Carlo Evaluation of HJM Models

### 2016-05-07 tests/HJM/manuscript.tex
complete pics 1

Overall, we may approximate a future price of a zero-coupon bond as
\begin{align*}
\mathcal G \parent f =
\expp{\expf{-\int_0^{t_{T}} f \parent{s,s} ds}\expf{-\int_{\tau_1}^{\tau_2} f \parent{T,\tau} d\tau}}
\approx
\underbrace{\expp{
F_{N_t,N_f}
\Psi_{N_f} }}_{\overline G_{N_t,N_f}}.
\end{align*}
Continuing the case of exponential covariance structure where $c_k \sim \bigo{k^{-2}}$,
we expect, based on the above computations, to observe the following rate
\begin{align*}
\expp{ \parent{\mathcal G - \overline G_{N_t,N_f}}^2} = \bigo{N_f^{-3} N_t^{-2}}.
\end{align*} 
To complement the component-wise plots in figures \ref{fig:rateFig1}, \ref{img:rateFig2} and
\ref{img:rateFig3}, we plot the overall approximation of $\mathcal G$ with $\overline G$
in figure \ref{img:rateFig4}.

>>>>

Overall, we may approximate a future price of a zero-coupon bond as
\begin{align*}
\mathcal G \parent f =
\expp{\expf{-\int_0^{t_{T}} f \parent{s,s} ds}\expf{-\int_{\tau_1}^{\tau_2} f \parent{T,\tau} d\tau}}
\approx
\underbrace{\expp{
F_{N_t,N_f}
\Psi_{N_f} }}_{\overline G_{N_t,N_f}}.
\end{align*}
Continuing the case of exponential covariance structure where $c_k \sim \bigo{k^{-2}}$,
we expect, based on the above computations, to observe the following rate
\begin{align*}
\expp{ \parent{\mathcal G - \overline G_{N_t,N_f}}^2} = \bigo{N_f^{-3} N_t^{-2}}.
\end{align*} 
To complement the component-wise plots in figures \ref{fig:rateFig1}, \ref{img:rateFig2} and
\ref{img:rateFig3}, we plot the overall approximation of $\mathcal G$ with $\overline G_{N_t,N_f}$
in figure \ref{img:rateFig4}.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr4.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr4.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Above: Weak (left) and strong (right) error
    for the temporal discretisation
    $\nnorm{\overline G_{65,2N_f}-\overline G_{65,N_f}}{}$,
    along with the $N_f^{-\frac{3}{2}}$ and $N_f^{3}$ reference lines (red).}
\end{figure}
